Toxic Code Snippets on Stack Overflow

### 2018-11-27 cloverflow-tse/cloverflow.tex
Updated Matheus's bio.

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mpaixao.png}}]{Matheus Paixao}
is currently a PhD candidate in the Computer Science Department at University College London, where he is part of the CREST centre.~He is supervised by Dr.~Jens Krinke, Prof.~Mark Harman, Dr.~Emmanuel Letier and Dr.~Yuanyuan Zhang.
His research interests include software architecture, search based software engineering, technical debt, empirical software engineering and modern code review.
\end{IEEEbiography}
%\vspace{-1cm}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mpaixao.png}}]{Matheus Paixao}
is currently a Research Assistant in the Computer Science Department at State University of Ceara. He recently received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group. He was supervised by Prof. Mark Harman and Dr. Jens Krinke. His research interests include software architecture, search-based software engineering, mining software repositories, modern code review and empirical software engineering.
\end{IEEEbiography}
%\vspace{-1cm}
